{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-08-19 paper/tex/sections/variations.tex
BIG COMMIT: lots of changes from Selma
update variations to match noBHkick models

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig7_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties. An arrow indicates that the error bar extends to zero. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}. See also Fig.~\ref{fig:dco_relative_rates} and Sec.~\ref{sec:detection_rate_analysis} for a discussion. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}. \todo{Will add R, T once Floor says that they are done}}
    \label{fig:detection_rates}
\end{figure*}

@@

\todo{Discuss $\alpha_{\rm CE}$ changes once I understand them (:}

@@

\todo{ensure this noBHkick description still applies} In model \modNoBH{} we do not give black holes natal kicks. Rate is higher than fiducial for BHBH and BHNS but slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick. NSNSs are unaffected as one would assume.

@@

\subsubsection{Using LISA to investigate the lower mass gap}

@@

% \begin{table}[htb]
%     \centering
%     \begin{tabular}{l|cccc}
%         \hline
%         \multirow{2}{*}{Component} & At Formation & \multicolumn{3}{c}{LISA detectable (4 year)} \\ \cline{2-5}
%         & All & BHBH & BHNS & NSNS \\
%         \hline
%         Low-$\alpha$ disc & 42.5\% & 88.6\% & 81.8\% & 84.9\%\\
%         High-$\alpha$ disc & 42.5\% & 5.2\% & 8.1\% & 12.0\%\\
%         Bulge & 15.0\% & 6.2\% & 10.1\% & 3.1\%\\
%     \end{tabular}
%     \caption{Percentage of systems in each Galactic component.}
% \end{table}

>>>>

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{fig7_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties. An arrow indicates that the error bar extends to zero. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}. See also Fig.~\ref{fig:dco_relative_rates} and Sec.~\ref{sec:detection_rate_analysis} for a discussion. \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
    \label{fig:detection_rates}
\end{figure*}

@@

\todo{Discuss $\alpha_{\rm CE}$ changes}

@@

In model \modNoBH{} we do not give black holes natal kicks. For BHBHs, the rate is approximately equal to that of model \modSigLower{} since kicks of $30 \unit{km}{s^{-1}}$ are equivalent to no kicks for massive BHs in our sample. For BHNSs, this model's rate is still well above the fiducial but decreases slightly relative to model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick. NSNSs are unaffected as one would assume.

@@

\subsubsection{Using LISA to investigate the lower mass gap}\label{sec:lower_mass_gap}

@@

\subsubsection{Effect mass loss rate multiplier on the (chirp) mass distribution}

{\bf Selma would like this one}
